\LARGE \bf Detection of design pattern : A systematic mapping study

### 2015-12-31 article/main.tex
Corrections, diagrams et a little more

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

@@

\author{Pierre Gerard, Alexandre Saint-Louis Fortier, Badr Mai and Houari Sahraoui \\
Département IRO \\
Université de Montréal, Montreal, Canada \\
\{gerardpi,Unknown,Unknown,sahraouh\}@iro.umontreal.ca
% <-this % stops a space
%\thanks{*This work was not supported by any organization}% <-this % stops a space
%\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
 %       University of Twente, 7500 AE Enschede, The Netherlands
  %      {\tt\small h.kwakernaak at papercept.net}}%
%\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
   %     Dayton, OH 45435, USA
    %    {\tt\small p.misra at ieee.org}}%
}

@@

Abstract goes here

@@

Introduction goes here
% pourquoi la detection

@@

The main goal of this paper is to determine the quantity and trends of research in design pattern detection and the quality of proposed detection methods.
\begin{itemize}
	\item \textbf{RQ1} : How mature is research on the subject of design pattern detection ?
	\item \textbf{RQ2} : What methods of design pattern detection are used ?
\end{itemize}

@@

We decided to query only one database, Scopus \cite{c2}, that claimed to be the largest abstract and citation database of peer-reviewed literature. It indeed index the main Computer Science databases : Springer, IEEE, ACM and others. The main advantage of doing so is that one could easily export result of an important number of publication from Scopus.

From the two research question we tried to maximise the number of publication found on the subject. To achieve that purpose we used for the query a disjonction of thesaurus for detection on their respective contracted form : detect*, recogni* and ident*. We have then added to the query a disjonction of pattern and motif.
We have limited the query to the abstract, the title, and keywords of each article.

We have limited our research to the year between 2000 and 2015 included.

We have also limited our research to the field of computer science and engineering.

The query resulted of a total of 403 articles. In those articles, we found two duplicates that we have immediately removed from the result.

@@

After having queried the database, we exported results found and process to screening.

@@

The aim of screening is to select papers relevant to design pattern detection. For that purpose, we used an exclusion scheme containing four criteria :

\begin{enumerate}
	\item \textbf{Not a contribution in software engineering} : this criteria also exclude articles that are not more than an use case of software engineering,
	\item \textbf{Not a full conference or research paper},
	\item \textbf{Not about software design pattern} : this criteria exclude articles where the main contribution is not about design pattern as defined in the Gang Of Four ,
	\item \textbf{The main contribution of the paper is not about detection of design pattern}.
\end{enumerate}

If in article matched more than one criteria, we assigned the lowest criteria to him.

@@

The inter-rater agreement cohen's kappa gave us the following result:
% citation needed

\begin{center}
  \begin{tabular}{ | l | c | }
    \hline
    Group 1 & 0.88 \\ \hline
    Group 2 & 0.66 \\ \hline
    Group 3 & 0.91 \\
    \hline
  \end{tabular}
\end{center}

It is usually said that a cohen's kappa coefficient of more than 0.7 indicate a good agreeement.% citation needed

@@

All of that leaded us to seven main categories.
% explication pour chaque catégorie
\begin{itemize}
	\item \textbf{Detection strategy} : 
	\item \textbf{Language generality} : This specifies if the detection is langage dependent or independent.
	\item \textbf{Analysis type}
	\item \textbf{Validation method}
	\item \textbf{Detection Level}
	\item \textbf{Detected pattern types}
	\item \textbf{Pattern detection generality}
\end{itemize}

@@

@@

>>>>

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{graphicx} % for png files
\graphicspath{{img/}}
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

@@

\author{Pierre Gerard, Alexandre St-Louis Fortier, Badr Mai and Houari Sahraoui \\
Département IRO \\
Université de Montréal, Montreal, Canada \\
\{gerardpi,stlouial,sahraouh\}@iro.umontreal.ca
% <-this % stops a space
%\thanks{*This work was not supported by any organization}% <-this % stops a space
%\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
 %       University of Twente, 7500 AE Enschede, The Netherlands
  %      {\tt\small h.kwakernaak at papercept.net}}%
%\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
   %     Dayton, OH 45435, USA
    %    {\tt\small p.misra at ieee.org}}%
}

@@

% Place holder

Lorem ipsum dolor sit amet, consectetur adipiscing elit. In pulvinar dui eget dignissim congue. Aenean interdum orci arcu, non varius nibh condimentum eu. Ut eget purus et purus pharetra egestas. Sed nec convallis lorem. Mauris fringilla velit est, elementum tincidunt lorem hendrerit ac. Vivamus et lorem nisi. Maecenas interdum diam id turpis aliquet lacinia.

Morbi rutrum tortor volutpat lacus lobortis interdum. Nam at mauris tristique, vulputate tortor non, egestas ex. Ut mauris libero, egestas at lacus sit amet, volutpat volutpat sapien. Quisque aliquet diam maximus lorem laoreet accumsan. Integer eleifend magna at nunc dapibus bibendum. Nam sagittis velit quis neque rhoncus, eget venenatis ante suscipit. Cras condimentum quam justo, quis pharetra nisi porta at. Sed sed ultricies dui. Sed id facilisis metus.

Maecenas feugiat augue purus, id interdum tellus sagittis at. Donec a orci sem. Aenean non elit maximus, fermentum odio et, mattis neque. Sed interdum in odio at egestas. Proin vel mi at elit congue lacinia et eu lectus. Praesent at rhoncus ante. Sed pulvinar tortor quis congue sagittis. Quisque tortor mi, semper vel rhoncus eu, sollicitudin et nibh.

@@

% Design patterns are a

Design partterns are best pratice to recurring problems proposed by the Gang
of Four in their seminal book.

(Some study author) have been able to show that the presence of design patterns
can help one better understand a piece of software.

Detection of design patterns in software has been a relatively active research
interest of the past decade in software engineering.
Proposed methods of automatic detection aims in part to facilitate the work of
developpers in understanding a piece of software through reverse engineering.

However, no studies have been conducted to analyse the trends of the field.

% pourquoi la detection

@@

The main goal of this paper is to determine the quantity and trends of research
in design pattern detection and the quality of proposed detection methods.
% Our classification scheme doesn't really allow us to take any position
% relative to the quality of the methods. At most, it provide a sensible
% evaluation of the field

\begin{itemize}
	\item \textbf{RQ1} : How mature is research on the subject of design pattern detection ?
	\item \textbf{RQ2} : What methods of design pattern detection are used ?
\end{itemize}

@@

We decided to query only one database, Scopus \cite{c2}, that claims to be the
largest abstract and citation database of peer-reviewed literature.
It indexes the main Computer Science databases : Springer, IEEE, ACM and
others.
The main advantage of using Scopus is that it provides a functionnality to
export the result of a search query on its database.
Some of those exported results would not have been easily obtainable on some
publishers search engines that do not provide an export functionnality.
Consequently, Scopus was used mostly as a Search and Export portal over the
relevant publications, greatly reducing the effort needed to extract the
original articles set. 
% TODO: Original articles set <- better wording?!

From the two research questions we tried to maximise the number of publications
found on the subject.
% Thesaurus is a synonym dictionnary... therefore a "disjunction of thesaurus"
% doesn't make any sense.
To achieve that purpose we used for the query a disjonction of thesaurus for
\textit{detection} on their respective contracted form : \textit{detect*},
\textit{recogni*} and \textit{ident*}.
We have then added to the query a disjonction of \textit{pattern} and \textit{motif}.
The query was limitied to the abstract, the title, and keywords of each article.
% Do we like oxford comma?

To limit the scope of our research only the articles published between the years
2000 and 2015 have been included.

% This sentence is not necessary... It is evident that we excluded other domains.
We have also limited our research to the field of computer science and
engineering.

The query resulted in a total of 403 articles.
Of those articles, we found two duplicates that were immediately removed from
the set of articles to analyse which brings down the number of articles for
screening to 401.

@@

% Problem with that sentence
After having queried the database, we exported the results found and process to
screening.

@@

The aim of screening is to select papers relevant to design pattern detection.
For that purpose, we used an exclusion scheme containing four criteria:

\begin{enumerate}
  \item \textbf{Not a contribution in software engineering}: 
    This criterion was used to exclude articles not relevant to the domain and
    software engineering articles that are nothing more than mere use case
    reports.
  \item \textbf{Not a full conference or research paper},
    This criterion was used to exclude small
  \item \textbf{Not about software design pattern}:
    This criterion excludes articles where the main contribution is not about
    design pattern as defined in by the Gang of Four ,
  \item \textbf{The main contribution of the paper is not about a method of detecting design patterns}:
    This criterion was used to exclude benchmarks and other analysis whose main
    purposes are not a method of design pattern detection.
\end{enumerate}

If in article matched more than one criteria, we assigned the lowest criteria
to it.

@@

The inter-rater agreement Cohen's kappa gave us the following result:
% citation needed

\begin{center}
  \begin{tabular}{ lcc }
    \bf Group & \bf \# of articles & \bf Cohen's kappa \\
    1 & ??? & 0.88 \\
    2 & ??? & 0.66 \\
    3 & ??? & 0.91 \\
  \end{tabular}
\end{center}

It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
a good agreeement.% citation needed

@@

All of that leaded us to seven main categories.

\begin{itemize}
  \item Detection strategy:
    This determine the means on which the detection is based.
    Possible values: Artificial intelligence, Logic/Formalisation, Graph,
    Metric, Automata, Instrumentation/profiling and Others.

  \item Language dependance
    This category aims to classify detection methods on wether it is dependant
    on the language or not. 
    Possible values: Dependant or Independant
% This  specifies if the detection is langage dependent or independent,

  \item Analysis type
    This determine if a detection techniques use a static, dynamic or hybrid
    approach.
    Possible values: Static, Dynamic and Hybrid.

  \item Validation method:
    This specifies the type of scientific validation methods the article's 
    authors used for a detection method.
    Possible values: Benchmark, Case study, Experiment, Survey, Other and
    None.

  \item{Detection Level}
    This define on which level the detection method work : execution, source
    and model.
    It could be more than one level for a single method of detection.
    Possible values: Execution, Source and Model.

  \item Detected pattern types :
    This characterizes the type of design pattern a specific detection method
    can manage.
    The possible values for this category are Creationnal, Behavioural,
    Structural and Not specified.

  \item Pattern detection generality :
    This determine if a method is made to detect a single pattern or more than
    one pattern.
    Possible values: Specific, General.
\end{itemize}

@@

% Need result table

\subsubsection{Year distribution}
% Need to change the title for this graphic

\begin{center}
\includegraphics[scale=0.75]{articles_by_years.png}
\end{center}

\subsubsection{Venue Distribution}
% Need a graphic for article by publishers.

\subsubsection{Detection Strategy}

\begin{center}
\includegraphics[scale=0.75]{detection_strategy.png}
\end{center}

\subsubsection{Analysis Type}

Design pattern detection can be done either statically or dynamically.

\begin{center}
\includegraphics[scale=0.75]{analysis_type.png}
\end{center}

\subsubsection{Detected Pattern Types}

The Gang of Four identified three design pattern types: creationnal,
behavioural and structural patterns.
Due to the nature of each pattern types, it is usally aknowledged that
structural patterns should be easier to detect than behavioural patterns and
that the later are easier than creationnal patterns (citation needed). 
It was expected that this ordering would appear in the number of articles
associated with each pattern types. 
However, we can see that the detection of behavioural patterns has been the
subject of more articles than the two others.

\begin{center}
  \includegraphics[scale=0.65]{pattern_types.png}
\end{center}

This can be explained either by the fact that structural design patterns
detection is considered as an easy problem, thus less likely to be the main
focus of a research papers or by the possibility is that behavioural design
patterns are in fact easier to detect than structural ones.
However, we believe the first possibilty to be more likely.

\subsubsection{Language dependance}

\begin{center}
\includegraphics[scale=0.75]{language_generality.png}
\end{center}

\subsubsection{Detection Level}

\begin{center}
\includegraphics[scale=0.75]{detection_level.png}
\end{center}

\subsubsection{Detection generality}

\begin{center}
\includegraphics[scale=0.75]{detection_generality.png}
\end{center}

\subsubsection{Validation Methods}

\begin{center}
\includegraphics[scale=0.75]{validation_method.png}
\end{center}

\subsubsection{Detected pattern types according to analysis type}
% Need graphics

%todo

@@

DATA

\section{Study limitations}

\subsection{Selection Bias}

A possible limitation of our studies is the selection of a unique source for 
the articles in Scopus.
This was done to facilitate our work in the extraction of relevant articles
since Scopus offers to export the results of a search query on its database.
It has been assumed that it does an exhaustive indexing of the journals
and conferences it references and that those sources includes most of the
relevant publications that covers software design pattern detection.
To mitigate the possibility of missing relevant articles we made sure that
Scopus indexes the big venues of software engineering (ACM, Springer, IEEE, and
???).

There is a possibility for relevant articles to have been excluded at the
screening level due to a non representative title and abstract.
We believe the possibility to be unlikely since each article were screened by
two reviewers and that if the article had a possibly misleading title, it would
be rejected after a complete reading done before the classification phase.

As it can be seen with Cohen's kappa coefficient of the second screening group,
there were some disagreement related to the inclusion or the exclusion of some
articles.
Most of those disagreement comes from different views of what constitute a
software engineering papers and the fact that many fields have adopted the
concept of design patterns.
Even if the Cohen's kappa coefficient can be considered somewhat low for the
second group, we are confident with our screening since most disagreement have
been resolved by an experienced researcher in the field if a pair of reviewers
couldn't reach a consensus.

\subsection{Classification}

At first, we defined the detection level to be a disjoint classification category.
However during the classification phase of our study, we stumbled upon unfoseen cases
where the detection was done at two levels. We had to change the classification
scheme to allow those cases.

\section{Related works}

So far, no other comparable studies has been done on the field of design pattern
recognition.

(article on method validation) have identified a problem in the evaluation of design
pattern detection methods. This problem has been observed in our evaluation of the
domain in that most articles evaluates their algorithms with case studies that are
hardly comparable.
